### 2021-09-09 manuscript/conclusions.tex
correcoes de texto e inclusoes de valores de desvio padrao

Comparisons between the estimated physical-property distribution obtained with our method and 
the classical approach that solves the least-squares normal equations via Cholesky decomposition 
show similar results. 
The differences in total number of floating-point operations (flops), memory usage and computation 
time, however, are noticeable. 
For a mid-size grid of $100 \times 50$ points, the total number of flops is about four orders of
magnitude smaller than that required by the classical method. Besides, our method uses
less than $1\%$ of the RAM and takes about $4\%$ of the computation time associated with
the classical method in this case. (TEM QUE CHECAR ESTAS VALORES)
Significantly better results can be obtained with larger data sets.

>>>>

Comparisons between the estimated physical-property distribution obtained with our method and 
the classical approach that solves the least-squares normal equations via Cholesky decomposition 
show similar results. 
The differences in total number of floating-point operations (flops), memory usage and computation 
time, however, are noticeable. 
For a mid-size grid of $100 \times 50$ points, the total number of flops is about four orders of
magnitude smaller than that required by the classical method. Besides, our method uses
less than $1\%$ of the RAM and takes about $3\%$ of the computation time associated with
the classical method in this case.% (TEM QUE CHECAR ESTAS VALORES)
Significantly better results can be obtained with larger data sets.
